---
title: Tedy Herlambang/mikroekonomi
output:
  xaringan::moon_reader:
    chakra: libs/remark-latest.min.js
  # self_contained: TRUE
    includes:
      in_header: conf/style-header.html
    lib_dir: libs
    seal: false
    css: ["default", "conf/css/style.css", "conf/css/fonts.css"]
    nature:
      beforeInit: ["conf/js/gifffer.min.js", "conf/js/style-macros.js"]
      ratio: 16:9
---
```{r, echo = FALSE}
# google scholar metadata
library(metathis)

if (knitr::is_html_output()) {
  meta() |> 
    meta_google_scholar(
      title = "Produksi dan Biaya dalam Perusahaan",
      author = "Tedy Herlambang",
      publication_date = "2021",
      isbn = ""
    ) 
}
```

```{r setup, echo = F}
knitr::opts_chunk$set(
  comment = "#",
  #cache = TRUE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 7,
  fig.height = 5.25,
  fig.align = 'center',
  fig.retina = 3
)

# base plot layout
mypar = list(mar = c(3,3,0.5,0.5), mgp = c(1.5, 0.3, 0), tck = -.008)

# xaringan Extra
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_panelset()
xaringanExtra::use_scribble()
```

class: middle, title-slide

<!-- top logo (comment to remove or edit on `conf/css/style.css:23`) -->
<div class="lab-logo"></div>
<!-- <div class="uni-logo"></div> -->

# Produksi dan Biaya dalam Perusahaan

<hr width="55%" align="left" size="1.3" color="orange"></hr>

## Mikroekonomi: Materi Minggu ke 9 

### Tedy Herlambang .small[<br>]

<br><br><br><br><br>
[<i class="fas fa-blog" style="color:#e7e8e2"></i> bangtedy.github.io](https://bangtedy.github.io)

[<i class="fa fa-twitter fa-lg" style="color:#e7e8e2"></i> @t_hlb](https://twitter.com/t_hlb)
---

# Capaian Pembelajaran

Setelah mempelajari bab ini, Anda diharapkan dapat:
- Membedakan dan menjelaskan tiga jenis keuntungan
- Menjelaskan fitur penting produksi dalam jangka pendek
- Menjelaskan mengapa biaya rata-rata mencapai minimum ketika MC=AC
- Menjelaskan sumber-sumber economies of scale dan diseconomies of scale
---
class: middle, center, inverse

# Biaya dan Keuntungan
<hr width="100%" align="left" size="0.3" color="orange"></hr>

---
# Cost and Profit

- With supply we assume that producers try to maximize profit, and this goal motivates their behaviour. 
- Firms try to earn a profit by transforming resources into products (goods/services). 
- Over time, firms that survive and thrive are those that are more profitable. 
- Unprofitable firms eventually fail. 
- Each firm’s decision makers must choose what goods and services to produce and what resources to employ. 
- They must make plans while confronting uncertainty about consumer demand, resource availability, and the intentions of other firms in the market.
  
---
# Biaya Eksplisit and Implisit

- Biaya eksplisit: opportunity cost of resources employed by a firm that takes the form of cash payments
- Biaya implisit: a firm’s opportunity cost of using its own resources or those provided by its owners without a corresponding cash payment

---
# Pengukuran Keuntungan

- Keuntungan akuntansi: a firm’s total revenue minus its explicit costs
- Keuntungan ekonomi (*economic profit*): a firm’s total revenue minus its explicit and implicit costs
- Keuntungan normal (*normal profit*): a firm’s accounting profit when all resources earn their opportunity cost; equal to implicit cost

---

class: middle, center, inverse
# Produksi dalam Jangka Pendek
<hr width="100%" align="left" size="0.3" color="red"></hr>

---
# Input tetap dan variabel (Fixed and Variable input)
- <span style="color:gold"> variable input</span>: any resource that can be varied in the short run to increase or decrease production
- <span style="color:gold">fixed input</span>: any resource that cannot be varied 
in the short run
- <span style="color:green">short run</span>: a period during which at least one of a firm’s resources is fixed
- <span style="color:green">long run</span>: a period during which all resources under the firm’s control are variable

---
# Law of Diminishing Marginal returns
- Produksi total (Total product): a firm’s total output 
- Fungsi Produksi (production function): the relationship between 
resources employed and a firm’s total product
- Produk marjinal (marginal product): the change in total product when a particular resource increases by one unit, all other resources constant
- Increasing marginal returns: the marginal product of a variable resource increases as each additional unit of that resource is employed
- Law of diminishing marginal returns: as more of a variable resource is added to a given amount of other resources, marginal product eventually declines and could become negative
---
# Kurva Total dan Marjinal Produk


---

class: middle, center, inverse
# Biaya Produksi dalam Jangka Pendek
<hr width="100%" align="left" size="0.3" color="red"></hr>

---
# Biaya Produksi dalam Jangka Pendek

- Biaya tetap (fixed cost): any production cost that is independent of the 
firm’s rate of output
- Biaya variabel (variable cost): any production cost that changes as 
the rate of output changes
- Biaya total (total cost): the sum of fixed cost and variable cost,or TC= FC + VC
- Biaya marjinal (marginal cost): the change in total cost resulting from a one-unit change in output; the change in total cost divided by the change in output, or MC = ΔTC/Δq
---
# Hubungan antara biaya marjinal dengan biaya rata-rata 

- Biaya tetap rata-rata (average fixed cost): fixed cost divided by output, 
or AFC=FC /q
- Biaya variabel rata-rata (average variable cost): variable cost divided by output, or AVC= VC /q
- Biaya total rata-rata (average total cost):total cost divided by output, 
or ATC =TC /q. Also the sum of average variable cost and average fixed cost, or ATC = AVC + AFC 

---


class: middle, center, inverse
# Biaya Produksi dalam Jangka Panjang
<hr width="100%" align="left" size="0.3" color="red"></hr>

---
# Skala ekonomi dan diseconomies of scale

- Economies of scale:forces that reduce a firm’s average cost as the scale of operation expands in the long run

- Diseconomies of scale: forces that may eventually increase a firm’s average cost as the scale of operation expands in the long run

---
#  Biaya rata-rata jangka panjang
- Long-run average cost curve: a curve that indicates the lowest average cost of production at each rate of output when the size, or scale, of the firm varies; also called the planning curve.

- Constant long-run average cost:  a condition that occurs if, over some range of output, long-run average cost neither increases nor decreases with changes in firm size
- Minimum efficient scale: the lowest rate of output at which a firm takes full advantage of economies of scale

---

class: inverse

.pull-left1[
<br>

.font70[A single study is never the end of the story; multiple studies are 
needed before we can reach defensible conclusions about social phenomena.] 

<hr width="100%" align="left" size="0.3" color="orange"></hr>

<br><br><br><br><br><br><br><br>

**Special thanks to**

Mahasiswa Agribisnis Angkatan '21
]

.pull-right1[
<br>
![:scale 71%]()
]
