---
title: Tedy Herlambang/mikroekonomi
output:
  xaringan::moon_reader:
    chakra: libs/remark-latest.min.js
  # self_contained: TRUE
    includes:
      in_header: conf/style-header.html
    lib_dir: libs
    seal: false
    css: ["default", "conf/css/style.css", "conf/css/fonts.css"]
    nature:
      beforeInit: ["conf/js/gifffer.min.js", "conf/js/style-macros.js"]
      ratio: 16:9
---

```{r setup, echo = F}
knitr::opts_chunk$set(
  comment = "#",
  #cache = TRUE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 7,
  fig.height = 5.25,
  fig.align = 'center',
  fig.retina = 3
)

# base plot layout
mypar = list(mar = c(3,3,0.5,0.5), mgp = c(1.5, 0.3, 0), tck = -.008)

# xaringan Extra
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_panelset()
xaringanExtra::use_scribble()
```

```{r, echo = FALSE}
# google scholar metadata
library(metathis)

if (knitr::is_html_output()) {
  meta() |> 
    meta_google_scholar(
      title = "MONOPOLISTIC COMPETITION AND OLIGOPOLY",
      author = "Tedy Herlambang",
      publication_date = "2021",
      isbn = ""
    ) 
}
```

class: middle, title-slide

<!-- top logo (comment to remove or edit on `conf/css/style.css:23`) -->
<div class="lab-logo"></div>
<!-- <div class="uni-logo"></div> -->

# MONOPOLISTIC COMPETITION AND OLIGOPOLY

<hr width="55%" align="left" size="1.3" color="orange"></hr>

## Mikroekonomi: Materi Minggu ke 12 

### Tedy Herlambang .small[<br>]

<br><br><br><br><br>
[<i class="fas fa-blog" style="color:#e7e8e2"></i> bangtedy.github.io](https://bangtedy.github.io)

[<i class="fa fa-twitter fa-lg" style="color:#e7e8e2"></i> @t_hlb](https://twitter.com/t_hlb)

---

# LEARNING OUTCOMES

After studying this chapter, you will be able to

- Outline the monopolistic and competitive elements of monopolistic competition
- Describe the sources of oligopoly and explain why some industries become oligopolies
- Explain why predicting oligopoly behavior is so difficult
- Summarize the similarities and differences between an oligopoly and perfect competition in terms of price, output, and long-run profitability
 
---
# INTRODUCTION

- Perfect competition and monopoly are extreme market structures. 
- Under perfect competition, many suppliers offer an identical product and, in the long run, entry and exit erase economic profit. 
- A monopolist supplies a product with no close substitutes in a market where 
natural or artificial barriers keep out would-be competitors, so a monopolist can earn economic profit in the long run. 
- These polar market structures are logically appealing and offer a useful 
description of some industries observed in the economy.
- But most firms fit into neither market structure. 
- This chapter examines the two remaining market structures that together 
account for most firms in the economy.

---
class: middle, center, inverse

# # MONOPOLISTIC COMPETITION
<hr width="100%" align="left" size="0.3" color="red"></hr>

---

> A market structure with many firms selling products that are substitutes but different enough that each firm’s demand curve slopes downward; firm entry is 
relatively easy

---

# Product Differentiation

- Physical Differences
- Location
- Services
- Product Image

---
# Short-Run Profit Maximization or Loss Minimization
- Marginal Revenue Equals Marginal Cost
- Maximizing Profit or Minimizing Loss in the Short Run

---
# Zero Economic Profit in the Long Run



---
# Monopolistic Competition and Perfect Competition Compared

---

class: middle, center, inverse

# OLIGOPOLY
<hr width="100%" align="left" size="0.3" color="orange"></hr>


---


class: inverse

.pull-left1[
<br>

.font70[A single study is never the end of the story; multiple studies are 
needed before we can reach defensible conclusions about social phenomena.] 

<hr width="100%" align="left" size="0.3" color="orange"></hr>

<br><br><br><br><br><br><br><br>

**Special thanks to**

Mahasiswa Agribisnis Angkatan '21
]

.pull-right1[
<br>
![:scale 71%]()
]
