---
title: Tedy Herlambang/mikroekonomi
output:
  xaringan::moon_reader:
    chakra: libs/remark-latest.min.js
  # self_contained: TRUE
    includes:
      in_header: conf/style-header.html
    lib_dir: libs
    seal: false
    css: ["default", "conf/css/style.css", "conf/css/fonts.css"]
    nature:
      beforeInit: ["conf/js/gifffer.min.js", "conf/js/style-macros.js"]
      ratio: 16:9
---

```{r, echo = FALSE}
# google scholar metadata
library(metathis)

if (knitr::is_html_output()) {
  meta() |> 
    meta_google_scholar(
      title = "Pasar Bersaing Sempurna",
      author = "Tedy Herlambang",
      publication_date = "2021",
      isbn = ""
    ) 
}
```

```{r setup, echo = F}
knitr::opts_chunk$set(
  comment = "#",
  #cache = TRUE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 7,
  fig.height = 5.25,
  fig.align = 'center',
  fig.retina = 3
)

# base plot layout
mypar = list(mar = c(3,3,0.5,0.5), mgp = c(1.5, 0.3, 0), tck = -.008)

# xaringan Extra
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_panelset()
xaringanExtra::use_scribble()
```

class: middle, title-slide

<!-- top logo (comment to remove or edit on `conf/css/style.css:23`) -->
<div class="lab-logo"></div>
<!-- <div class="uni-logo"></div> -->

# Pasar Bersaing Sempurna

<hr width="55%" align="left" size="1.3" color="orange"></hr>

## Mikroekonomi: Materi Minggu ke 10 

### Tedy Herlambang .small[<br>]

<br><br><br><br><br>
[<i class="fas fa-blog" style="color:#e7e8e2"></i> bangtedy.github.io](https://bangtedy.github.io)

[<i class="fa fa-twitter fa-lg" style="color:#e7e8e2"></i> @t_hlb](https://twitter.com/t_hlb)

---

# CAPAIAN PEMBELAJARAN

Setelah mempelajari bab ini, Anada akan mampu:

- Describe the market structure of perfect competition
- Determine the perfectly competitive firm’s profit-maximizing output in the short run
- Outline the conditions under which a firm should produce in the short run rather than shut 
down, even though it incurs an economic loss
- Describe a perfectly competitive firm’s short-run supply curve
- Explain why in perfect competition, there are no economic profits or losses in the long run
- Explain why, in some perfectly competitive industries, market supply curves slope upward in the long run
- Summarize how market equilibrium in perfect competition results in productive efficiency and allocative efficiency
---
# AN INTRODUCTION TO PERFECT COMPETITION

- Market structure: important features of a market, such as the number of firms, product uniformity across firms, firm’s ease of entry and exit, and forms of competition.

- Perfect competition: A market structure with many fully informed buyers 
and sellers of a standardized product and with no obstacles to entry or exit of 
firms in the long run

- Commodity: A standardized product; a product that does not differ across producers, such as a bushel of wheat or an ounce of gold

---
# Demand Under Perfect Competition

- A perfectly competitive firm is so small relative to the market that the firm’s supply decision does not affect the market price
- Demand curve facing an individual farmer is, therefore, a horizontal line drawn at the market price
- A perfectly competitive firm is called a price taker because that firm must “take,” or accept, the market price—as in “take it or leave it.”

---

# SHORT-RUN PROFIT MAXIMIZATION

- The firm maximizes economic profit by finding the quantity at which total revenue exceeds total cost by the greatest amount
- Marginal revenue (MR) The firm’s change in total revenue from selling an 
additional unit; a perfectly competitive firm’s marginal revenue is also the market 
price
- Golden rule of profit maximization: To maximize profit or minimize loss, a firm produces the quantity at which marginal revenue equals marginal cost; this rule holds for all market structures
- The firm increases production as long as each additional unit of output adds more to total revenue than to total cost—that is, as long as marginal revenue exceeds marginal cost
- in perfect competition, marginal revenue is the market price
> Market price = Marginal revenue = Average revenue
---

class: inverse

.pull-left1[
<br>

.font70[A single study is never the end of the story; multiple studies are 
needed before we can reach defensible conclusions about social phenomena.] 

<hr width="100%" align="left" size="0.3" color="orange"></hr>

<br><br><br><br><br><br><br><br>

**Special thanks to**

Mahasiswa Agribisnis Angkatan '21
]

.pull-right1[
<br>
![:scale 71%]()
]
